Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-12-05 Documents/Paper/ms.tex
evidence --> marginal likelihood

Some authors have addressed these kinds of problems by
doing separate runs of Nested Sampling
(or another method),
with $N$ fixed at various trial values \citep[e.g.][]{fengji, feroz}.
Then, the posterior for $N$ can be calculated
based on the estimates of the evidence obtained as a function of $N$.
This approach does not generalise well to large $N$, as it would
require a large number of parallel runs.

>>>>

Some authors have addressed these kinds of problems by
doing separate runs of Nested Sampling
(or another method of calculating marginal likelihoods),
with $N$ fixed at various trial values \citep[e.g.][]{fengji, feroz}.
Then, the posterior for $N$ can be calculated
based on the estimates of the marginal likelihood obtained as a function of $N$.
This approach does not generalise well to large $N$, as it would
require a large number of parallel runs.
